\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
almost2.0

Legitmate windows update from Ikai CDN 
DNS for onion domain Singapore 
DNS for cryptostorm to establish VPN Germany
Get Windows-CryptoAPI from comodoca 
China DNS req  for 1.83.255.178

@@

% DAN
On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence from what appears to be a span mail. A mail with an attachment, potentially a Microsoft Word document, is fetched after a "503 Backend fetch failed" response. The following request is made to a destination IP associated with an onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those circumventing censorship but also those who exploit it for profit. The ".link" allows for for convenience at the expense of privacy, as your service provider can see your what content you are requesting \cite{onionlink}. The host also visited  torstorm.org domain, which offers a similar service. This allowed the target system to visit a TOR hidden services hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of a malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}. Please refer to appendix A for the TCP conversation of the payload delivery.

@@

Next we see a query for the domain cyrptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. Cryptostorm uses openVPN to establish a secure VPN connection. The target host uses TLS to tunnel the openVPN connection to avoid blocking of the protocol. This is a feature provided by Cryptostorm which encrypts the TCP handshake to obscure the openVPN traffic \cite{tls}.

@@

The target host ceases to exist on the networking failing to respond to even ARP broadcasts from this point fordard.

@@

>>>>

@@

% DAN
On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence from what appears to be a spam mail. A mail with an attachment, potentially a Microsoft Word document, is fetched after a "503 Backend fetch failed" response. The following request is made to a destination IP associated with an onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those circumventing censorship but also those who exploit it for profit. The ".link" allows for for convenience at the expense of privacy, as your service provider can see your what content you are requesting \cite{onionlink}. The host also visited  torstorm.org domain, which offers a similar service. This allowed the target system to visit a TOR hidden services hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of a malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}. Please refer to appendix A for the TCP conversation of the payload delivery.

@@

Next we see a query for the domain cryptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. Cryptostorm uses openVPN to establish a secure VPN connection. The target host uses TLS to tunnel the openVPN connection to avoid blocking of the protocol. This is a feature provided by Cryptostorm which encrypts the TCP handshake to obscure the openVPN traffic \cite{tls}.

@@

The target host ceases to exist on the networking failing to respond to even ARP broadcasts from this point forward.

@@

%\lstinputlisting[language=html]{evilstats.txt}
